\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updating everything

@@

\begin{figure}
\centering 
%\begin{minipage}{1.0\textwidth}%
%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
%\end{minipage}%
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}. The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns. While there 
is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
\label{fig:vel_magn2}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%
\begin{figure}
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
}}%
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d).,followed by the t=1500(a,b), t=3000(c,d) in fig.\ref{fig:2btestcase}.}
\label{fig:2atestcase}
\end{figure}

\begin{figure}
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
}}%
\caption{When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2btestcase}
\end{figure}

@@

\begin{figure}
%\center
%\begin{minipage}{1.0\textwidth}%
%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
%\end{minipage}%
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}. The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns. While there 
is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
\label{fig:vel_magn2}
\end{figure}
